\indent As a child he suffered from severe asthma. The fits would come weekly, exacerbated by his nervous and jittery disposition. It would start with a cough --- maybe he had walked up the stairs too quickly, or maybe he had inhaled some dust --- and then the cough would split to two, four, then eight, growing exponentially like bacteria in a dish. Soon he couldn't breath, he could only gasp. Usually he would start crying too.
 
His solace came from mother and father; they would take him to his bathroom and turn on the shower at full heat. He would sit on mothers lap on the toilet as the scalding water hit the sides of the bathtub, the small droplets vaporizing into steam, and the steam then filling the shower before finally spilling out over the top of the curtain and descending onto them. The warm humid air and parental comfort surrounding him would finally cause his racking hacks and coughs to slow. They would all sit together silently until his breathing steadied and his fit subsided.
	
He outgrew the asthma for the most part, but the affliction stayed married to him in grief. His lungs were no longer prone to the intermittent attacks, but something deeper was still stricken with the tightening chest and gaspy breathing from his childhood.
	
In 8th grade his first “love” broke up with him and he found himself in a fit of immature agony on the floor of his room, gasping and crying, each shallow breath catching somewhere deep in his ribcage. It had been a few years, but he somehow knew that the steam would bring him relief. He stayed in the bathroom for an hour before mother and sister came in. They all sat in silence for a time, then went to his favorite restaurant and all was well.

The news about his mother’s passing just came and now he finds he has stumbled to his bathroom like always. This wasn’t unexpected like father’s was; late 80s is a full life. But the familiar gasping and tremors rack through him again as he turns on the water. He sits on the toilet and waits for the vapor to come. He can already see the cloudy wisps reaching up and over the shower curtain when he hears a knock on the door; his wife calls out to him. He can’t respond but she quietly enters anyway, closing the door behind her with a soft click. She sits by his side with a hand on his leg and together they wait for the cleansing steam to descend over them.
