“What do you want to do tonight?”
\\\\
Jane’s words were spoken from the same lips, the same mouth, with the same timbre and cadence as always. The way she always started her sentences out with strong, harsh syllables, before calming herself down to a mellow flow near the end.  This past week, however, her words sounded different to Zack. They made him nervous, as if there were something subtle going on behind her superficial sentences. He felt like at any moment he would say the wrong thing and something terrible would happen. Zack chose his words with care.
\\\\
“Oh, I have nothing serious planned”
\\\\
He tried to keep his response cool and casual, not wanting to incite the monstrous force beneath Jane’s words any further, but he was afraid that a distinct and involuntary tremor in his voice had just given away his fear. His eyes darted to the side, sneaking a quick glance at the pale woman beside him. She was engrossed in her phone for the moment and seemingly hadn’t noticed his stutter. He knew Jane was considered beautiful by most people and he was usually in agreement. Utilizing her moment of distraction, he stared at her hands. She was wearing that lime green tank top which he knew was her favorite because it brought out the darkness of her eyes. She looked up.
\\\\
“We could watch a movie”
\\\\
\textit{A movie}, he thought, what could she possibly mean by wanting to watch a movie. He knew that somehow her suggestion had a deeper context, one that hinted at terrible things, attempting to draw him into a trap of admission. But he wouldn’t give in. He couldn’t. Not yet. Even if it came as a surprise to her, it would be too hard to deal with right now. 
\\\\
“But we did that last night”
\\\\
A perfect counter. Zack had to consciously keep himself from putting on a smug look as he said it, and even then he suspected that if Jane had been paying more attention to him she would have seen a hint of gloating washing over his countenance. People love the cliché that conversations are like a game of tennis; well they are more like a game of lob-the-bomb-back-and-forth, a twisted mix of hot potato and Russian roulette. At any second she could throw one that he was unprepared for and win this weeklong struggle. He knew she knew anyway. But, on the chance she didn’t he had to keep playing the tiresome game of verbal jousting, staying ever alert to the subtext of it all.
\\\\
“There are lot of movies”
\\\\
\textit{Ahh Christ}. He flinched internally; this one wasn’t even subtle. There are a lot of movies and there are a lot of women out there in the world. He got the message loud and clear. So she knows. Of course she knows. He always knew she knew. She knew he had gone out, she saw the gaps in texting, she had seen the guilt somewhere behind his eyes. So why hasn’t she said something about it? If she wanted to play it this way, he was game.
\\\\
	“But only a handful of good movies”
\\\\	
That’s right just a handful of good movies. \textit{You are a good movie Jane}. He hoped she understood that one. \textit{You are a good movie and I hope you forgive me}. He risked another glance down over the warm body under his right arm, her dark hair tangled up on his shoulder, her back pressed firmly into his side. He could feel the pattern of her breathing and made an effort to slow his breaths to match hers. He had been breathing unusually fast. Why wouldn’t Jane just yell at him already? Slap him across the face and scream that she knew what he had done, that he was an asshole and that she was leaving forever, goodbye and have a nice life. That would make it so much easier; begging for forgiveness is a much lesser task than admission of guilt. He couldn’t live in limbo like this. The purgatory.
\\\\	
	“I’m sure we can find a good one tonight”
\\\\	
He didn’t deserve this much torture for a simple mistake. Fine, a few simple mistakes. Getting drunk was the first. Going to the same bar as Lauren was the second, although that was more happenstance than his fault really. He wanted to say that she kissed him first, he wanted to say that she was the forward one and that he was so lost in the throes of liquor that he didn’t even know what was going to happen. But none of that was true. He knew exactly where the evening was going the moment they saw each other. There was a spark in their gaze when he glanced over and caught the familiar face. Something like a shared smirk or a devilish grin that communicated more than any small talk, medium talk, or heavy talk could ever compare to. \textit{Oh hey haven’t seen you in ages} was actually a code; a code only they could speak and decipher. The rough translation is \textit{let’s make some memories and some mistakes together tonight.}
\\\\	
“Fine, what do you want to watch?”
\\\\
He thought that the morning after was going to be the worst part. Waking up hungover in the bed that he and Jane usually shared with essentially a stranger, both of them knowing that something had happened that could never be undone or forgotten. After letting her out of the apartment he thought that guilt would start to fade, start to become a thing of the night that could be tied to a rock and placed deep in the attic where he wouldn’t stumble upon it for a while. But it grew and it grew, a Chimera of shame that fed off his blurry memories from the night before. The beast chewed up the giddy laughter as they left the bar, holding hands for a moment then quickly letting go. It feasted on the shared excitement when they returned to Zack’s apartment, both of them repulsed yet so turned on by the dirtiness of their actions. When Zack began washing the sheets after Lauren left, the creature jabbed a paw into his heart. Every moment he was with Jane, the monster became stronger and more powerful, jaws clenching around something deep within him. Last night she had slept over, and as Jane fell asleep in his arms, he felt the monster pressing down on top of him, making it hard for him to breath. 
\\\\	
“Annie Hall?”
\\\\
He had to tell her. Even if she knew, she was never going to confront him. That’s how Jane worked. He had to tell her he was sorry, he had to tell her it wouldn’t happen again, he had to tell her that he wanted to be with her one hundred percent, now more than ever. He would be telling the truth, too. The passion of his night with Lauren was a magician’s flash paper. It had burned so bright, pure, and clean that he hadn’t been able to look away, he had to take it in before it burned itself to nothing at all. But with Jane he had a blaze; not as intense or bright, but deep and developed, a fire that had the potential to outlast both of them. He knew this and she hoped that she knew this.
\\\\
“Haven’t we both seen that?”
\\\\
He began preparing himself to say the words that had been on his mind for the past week. \textit{Jane I cheated on you}. He had said it in his head a million times, how different could it be to vocalize it. He shifted slightly as the Chimera in his chest started running around in terror, as if it sensed that it would no longer have a home within him. If he phrased it well enough she would forgive him, he mused, she has to forgive me. Jane looked into his eyes.
\\\\	
“Your point being?”
\\\\
As he met her gaze he knew better. If he told her –- if he removed all doubt from her mind that it had happened –- they wouldn’t last. He knew Jane, and he knew that she would not stand to stay with a cheater. And he couldn’t lose her. No, he couldn’t bear that. Nor could she for that matter. She needed him just as much as he needed her. So he would bear it. He would bear the guilt for both of their well-being. He clenched his teeth as his monster curled up and went to sleep below his heart. It knew that it would be fed for a time to come. He smiled softly at Jane.
\\\\
“Ok, put it on”
\\\\
She picked up the remote to play the film and he drew her closer.