Having graduated from a prestigious university with a golden certificate stating that I, in all my hoity-toity and supercilious glory, had received a much coveted degree in literature, I sat down to begin what I only assumed would turn out to be the next great American novel. I spent the first month in what I thought of as the research phase, holed up in the attic room of my parents’ house, pouring over the greats.  I had dreams of writing a story with the creativity of Borges, the characters of Marquez, and the adventurous spirit of Cervantes. Each day took on the same monotonous trope: wake up with a cup of black coffee, read, eat, read, go for a walk around the block to re-calibrate my mind, read, cup of chai tea with cream, read, eat, read, sleep. The monotony, however, would only be apparent to an outsider. I would start my day gallivanting about in a small village in La Mancha, by lunch I would find myself braced against the dusty winds of Macando, and by evening I would be lost in the whimsical world of Orbis Tertius.

My novel, I knew, would revolve around a character. Someone so emotionally complex that writing the story would be an afterthought to creating a person so profound. She would be a she, I decided, but I could not yet think of a name so I resolved to call her Zu until an appropriate title for such a woman presented itself to me. Slowly, as I read novel after novel, the essence of Zu began to form in my mind. An inchoate flurry of emotions and beliefs started to coalesce into cells, the cells dividing over and over to form more concrete ideas, a tangible personality even. As the concept of Zu became more real, her character expanded past the literary bounds from which I was drawing inspiration. She began acquiring her own childhood memories, then memories of her times in high school and college. All of the past events in her life explained who she was, what her dreams were, and where she wanted to go with her life. Her history also left her with numerous demons to bear, and in many ways, I pitied her.

With the essence of Zu swirling around my head, I started to write. The narrative began in a chilly apartment room in quasi-Chicago sometime in the past century. Not exactly now, because there were no cell phones or email, but not exactly the younger decades of the twentieth century either.  In fact, I really meant the setting to be some ambiguous metropolis, an amalgamation of your average American city, but I knew that some semblance of a link to my home would sneak through my writing.
\\\\
\textit{Zu celebrated her 26th birthday alone. She sat on the cool concrete of her balcony overlooking the city from 54 stories up, the cold surface gradually leaching the heat from her body, and by the time her watch clicked forward past midnight, she was shivering. A lightning storm had been illuminating the buildings around her for the past hour; each intrusive crackle made her flinch ever so slightly.}
\\\\
	The beginning of the book flowed out of my fingers effortlessly. As Zu sat, she smoked a cigarette and contemplated her life, the perfect vehicle to give the story some exposition. I slowly introduced the readers to this woman, hinting at her turbulent and tragic past, yet letting them guess at the deepest and darkest details. The cigarette lasts for two chapters, and at that point I decided to dive into the main arc. Introduce John. They meet at a bar, brought together by a work friend of Zu’s.
\\\\	
\textit{	Dark hair, even darker eyes. From the first glance Zu knew that something was going to be different about him. Perhaps it was the way he looked at her, a look that pierced deeper than the world of the shallow glances she was used to. Staring back she was able to see within him as well. She could decode the tentative fake smile, erased and then replaced by just the slightest glimmer of something real. This man had stories, demons; he was someone she could relate to.}
\\\\	
	They hit it off immediately, talking about themselves, their dark views on life, comparing the myriad of anti-anxiety and anti-depression cocktails they had both been on. It was in no way a normal courtship. They ended that first night with a kiss at the door of the bar, and a promise of a real date to come. 
\\\\	
	\textit{As he walked away, Zu licked her lips and her heart continued to beat loudly in her ears. The kiss had tasted like a mix of vanilla chapstick and vodka tonic. She sighed, ducking back into the bar to retrieve her coat.} I’ll see you soon\textit{, she whispered, echoing his last words to her. Her smiled lasted until she walked out into the brisk city air, when the memories of her past few ‘relationships’ assaulted her with pessimistic quips:} It won’t last. \textit{The words surrounded her, spoken by an army of recollections of failed attempts with other men. The barrage of memories all boiled down to the crucial point that it was always her fault. But this one will be different, she thought to herself, this one won’t fizzle like they all have. She put her head down and began the mile and a half walk back to her apartment.} 
\\\\	
	I found the beginning of their relationship easy to write. The chapters were filled with intense dialogue as they met up again and again for strange dates; one time just a walk by the lake at 3am, another time they simply drove in a 200 mile loop around the city. The dates were always at unusual times, late at night mostly, and they never cared what they were doing as long as they were able to talk uninterrupted for however long they pleased. One of their favorite things to do was to sit on Zu’s balcony and look down over the swath of illuminated windows scattered below them, making up twisted backstories and tangled drama for the people within.
\\\\	
	\textit{“There, how about that one?” John murmured, as he motioned towards a lit window in Zu’s neighboring building. Inside she could see an Asian man, probably in his late 50s, and a younger redheaded girl with a bow in her hair. The two of them were bent over, intently staring at the strange board game in front of them while the TV flashed Looney Toons behind them.}
	
\textit{“Well they are obviously lovers,” Zu spoke. }
	
\textit{	“Lovers?? I was going to say father and daughter.”}
	
\textit{	“Oh, so she’s adopted? They could still be lovers”}
	
\textit{	John snorted at that one, “You’re a sicko, you know that, right?”}
	
\textit{	Zu giggled and elbowed him in the ribs. “Ok then you try to do an interesting one then, it’s harder than it looks.” She paused and surveyed the valley of civilization below. “There, do that one.” She pointed up to another building, this one had a huge window on the top floor, and they had a great view of the scene within. Two men in suits were seated at the tables, unsmiling, discussing what must have been a morose matter. To their right was a couch, and on it sat a man and women, each of whom had a drink in hand. They, at least, were having a far lighter conversation by the looks of it.}
	
\textit{	“Ahhh, of course,” John whispered, “I know exactly what’s going on here. You see this is a love pentagon.”}
	
\textit{	“A love what?”}
	
\textit{	“Pentagon” he said, with mock exasperation, “It’s like a love triangle but with two more people. So men A and B, the ones sitting at the table, they both love woman C, the one on the couch. But man D from the couch, he loves man A. And woman C is actually in love with woman E, who isn’t even here. Woman E, of course, she isn’t in love with any of them, she just loves the drama.”}
	
\textit{	Zu couldn’t help but smirk. “Really? You are sure about all of that? Well why are A and B in such a bad mood, but C and D seem happy.”}
	
\textit{	John paused, “Well clearly A must have just proposed to C, and now B is jealous and confronting him. C and D have decided that the only thing to do here is drink and that is precisely why they are happier than A and B.”}
	
\textit{	Zu didn’t respond, but she snuggled up into him just a bit more so he knew that she appreciated the story. They sat in silence for a while, just content to be in each other’s presence. Every so often the breeze would pick up and they would catch a whiff of some food truck down on the street, seemed like it was the season for gyros.}
	
\textit{	“You know,” John began slowly, “That’s really life’s biggest tragedy, isn’t it?”}
	
\textit{	Zu looked up into his face and waited for him to continue.
}
	
\textit{	“All these people, in all these rooms.” He paused. “They all have stories.”}
	
\textit{	“Yeah, but we know all their stories, right?” Zu smiled as she said it.}
	
\textit{	“No like real stories. They have real lives behind their windows, real problems and emotions and real everything.”}
	
\textit{	“Everyone has those things.” As she said it, John looked even more serious, like she was missing some huge point that he was trying to allude to. She felt like she was back in high school, trying to pick the message out of some obscure and indirect text.}
	
\textit{	“Doesn’t it ever get to you? When you hold the door open for someone, or nod hello to a stranger on the train? Their life is as real to them as our lives are to us.” He seemed frustrated. Like he wasn’t able to articulate something that he had wanted to say for a while. “Every single person out there has a story, a long one; it’s got hundreds of characters, lots of ambition, dreams, intrigue, tragedy, you name it. And in my story they will just be the extra, the one in the background as I get my breakfast tomorrow. We will never be able to understand anyone to the same degree that we understand outselves.”}
	
\textit{	Zu was quiet for a moment, “I think understand,” she purred, pushing herself even harder into his side. “Let’s go inside.”}
\\\\	
	There relationship, however, was not a perfect one, far from it. Neither one them was a particularly happy person, and each would have little episodes where they would disappear, go incommunicado for a week or two. When it happened, neither tried to push the other; they both knew that only time could cure the oppressive weight of a depressive episode. They weren’t taking their prescribed drugs anymore. After a particularly powerful talk about overmedication and being in control of life, they both flushed away the rest of their pills; Xanax and Celexa for Zu, Prozac for John. 
	
	And then, without a hint of warning, my writing ground to a sickening halt. The words, which I had been so easily picking one by one out of my mind, were now lost to me. I would type a section, read over it, and delete it without a second thought. I tried asking myself what Zu would do next, how she would want to move forward from where she was, and I had no answers. Her motivations were lost to me. After being inside her head for so long I was terribly struck with the realization that she was not mine in the way she had been at the beginning of the story.
	
	For a week I wrote nothing. I sat, brooding at my computer, pouring over my past words, trying to find, from within my writing, the being that I had created so meticulously that at one point I thought I knew her better than myself. But she was a stranger to me.
	
	I got drunk one night off gin. I shut my computer down in disgust and drank from the bottle until my vision swam. I finally took a last swig then stumbled to my bed, sleep came much easier that night than it had all week. Waking the next morning, I was struck with the strangest of feelings that I had just been talking with an old friend. I didn’t think much of it at the time; I was well acquainted with some of the stranger effects of alcohol. But still I was left with a twinge of curiosity over what had happened for I, more than most, believed in the power of dreams to reveal our subconscious to us. The next morning, I was struck once again with the same feeling, this time my mind was completely clear of any semblance of a hangover.
	
	I had trouble getting to sleep the next night out of apprehension. I tossed and turned, checking the time every five minutes, and ended up wandering around the house at two in the morning with a cool glass of water, pressing it against my forehead and wondering what was going on. After getting back into bed, I was finally able to drift off, and within moments of passing into the realm of sleep, I found myself sitting on a familiar balcony overlooking a teaming metropolis below. I looked to the left and saw the Asian man and his redheaded daughter-lover still playing their alien board game. Then to the right I saw the members of the love pentagon watching Dead Poet Society together; much to my surprise it looked like the mysterious woman E had shown up. I looked back to the dark city and sat for a timeless interval; I knew she was coming.
\\\\	
	\textit{Hello}, she murmured, sliding the balcony door closed as she came through. Her voice was a little lower than I had expected. \textit{Hello Zu}, I responded. And so it began. That first night we talked for hours; she was as curious about me as I was about her. I told her stories from my childhood, about my parents and siblings, the middle school bully, my first serious girlfriend. And she delved into more detail about her own background, telling me stories of her youth and upbringing. Her father left when she was three, her mother was sickly until she died on Zu’s first day of high school, her godmother was abusive. I knew this all, of course, but hearing it from her lips had so much more gravity. I was in orbit around her, intoxicated with the tragedy of her past that I had created.
\\\\	
	When I woke, I rushed to my computer and added many more details to the earlier chapters. Hearing the stories from Zu herself helped me articulate the torments that her past had put her through. I finished this embellishment by evening, and crawled into bed as early as I would allow myself to. That second night we talked inside her apartment and discussed her feelings for John and where she saw the relationship going. I was surprised by how deeply she cared for him, having misjudged how much it meant to find someone to whom she could relate on the darkest of levels. I knew from this encounter to start moving their relationship forward, start escalating the time they spent with each other until they were almost inseparable.
\\\\	
\textit{	Zu was reluctant to end the embrace, but she finally released her grip. Goodnight Zu, he crooned as he turned to walk back to his apartment.} 23 dates, \textit{she thought to herself, but who’s counting. Zu had not thought it possible to be this happy. She had resolved herself to a life of disappointments and failed flirtations, but now it was all changing. John was changing it. In the months to come, Zu would remember this as the happiest time of her life, cherishing the memory just as much as she desperately yearned to have it back again.}
\\\\	
	Zu and I continued to meet every night for the next few months. We would spend an unknowable amount of time discussing her life, my life, life in general, and then I would spend the next day writing a few pages based on our encounter. Some nights we would talk in the fictional city of my novel, reliving the settings that I had so carefully constructed and written. Other nights we would hold our conversations in my world, the real one. We visited my old elementary school, my grandparents’ house, my freshman year dorm. Anything that was on my mind during the day usually became and artifact of the dreamscape. Several times we found ourselves in an indiscriminant location filled with a dense white fog in all directions, and once we ended up in the middle of some endless body of water, floating on a rickety raft made of four logs and some tarp. That was a fun spot to talk until we began seeing fins circling around us.
	
	Then one night, which would be the first of many, we came to be in a small cozy room that held only a lamp and a bed. The walls were a warm red, and the bed had baby blue sheets. I’d like to say that I was surprised at the setting, but if I were being honest with myself, I would have to admit that I was in love with her long before that first time.
	
	A month after this encounter, we were lying in the top bunk of my bed from camp; the shouts of a younger version of me playing with my friends could be heard through the canvas walls. Zu was gently tracing a path along my collarbone with her finger. \textit{John knows something is wrong}, she whispered. I twinged with guilt as she said it. I never explicitly stated that Zu was having an affair in my novel, but it slowly became obvious in her regular musings and monologues that she was becoming preoccupied with something. And now John could tell, he could feel her drifting away.
\\\\	
\textit{	“Are you ok?” John voice quivered with genuine concern.}
	
\textit{	“Yeah, I’m fine” Zu muttered, but she did not look up at him. Instead she started at the Asian and redhead playing that board game. How fucking fun could one game be that you would want to play it every night, Zu mused to herself, at least mix it up sometimes. She was pressed tightly against John, as she always was when they spent time on her balcony, but tonight she felt chilled. She shivered.}
	
\textit{	“Are you cold? Do you want to go inside?”}
	
\textit{	“No,” she responded, “Let’s stay out here for just a bit longer.” In reality Zu was scared of falling asleep with John tonight. She had been having trouble sleeping lately, and didn’t want to bother John with her insomnia. On the rare occasion that she fell asleep quickly, she would wake in the middle of the night upset for some reasons, but not knowing why. }
	
\textit{	“Ok, just let me know” John with just the tiniest hint of ice in his voice. He pulled his arm back from around her shoulder and placed it in his lap.}
\\\\	
	I considered ending my relationship with Zu, but that would have been too hard for me. We had reached a level of connection that I didn’t think possible, and I knew that it would hurt too much to go from where we were back to her just being a character of mine. Perhaps it was a type of love that could only be achieved in our strange situation; I believe that no one can love someone or something as much as what comes out of his own mind. And besides, her ambiguous reservations with John were driving the plot of my novel forward; it was turning into the complex emotional drama that I coveted.
	
	The rift between John and Zu was clearly expanding, although it seemed that she herself was oblivious to it. Their conversations started to evoke a suspicious tone, as if something were lurking beneath the words. Then one night Zu came running into my room in panic. \textit{It’s John}, she cried,\textit{ I don’t know where he is}. I hesitated, for I knew something like this was coming. \textit{Don’t worry}, I demurred, \textit{it’s just one of his episodes, this has happened before}. But somehow I knew she didn’t quite believe me; how could she really? She and John had stopped the silent periods a long time ago, when they had decided that, even at their worst, they were better together. But now the silence stretched longer than it ever had.
	
	For the first time in months I wrote a scene before Zu revealed it to me. He was found in his apartment after the landlady heard a shot. His body was taken to the morgue where it stayed, unclaimed, for the maximum waiting time of two weeks, and was then cremated. Zu had to learn of all this secondhand when she finally decided to go looking for him at his apartment. 
\\\\	
\textit{	“No.” Zu quivered, “no.” More quietly this time.}
	
\textit{	“I’m so sorry.” The wrinkled face of the landlady betrayed very little emotion. But her voice seemed to have some empathy. Zu sat down on the bench in front of the complex and put her head in her hands. The landlady shuffled away awkwardly, not wanting to intrude on Zu’s grief, which, in her opinion, was the most deeply personal of emotions.}
\\\\	
	I was scared as I got into bed that night; I didn’t want to face Zu. My fear, however, was for naught, as she was nowhere to be found in my slumber. Nor was she anywhere I looked the following night. Once again my writing came to a jarring halt; I needed to hear her reaction to his suicide to know what to say about it.
	
	For a week she was lost to me. I would spend my nights running around my dreamscapes, frantically trying to deduce where she might be hiding. Finally one night I felt a pull somewhere in my chest, tugging me in the right direction. I ran and I ran until my lungs were inflamed. As I turned the corner near her building, the air became viscous around me, and my forward progress began to slow. I pitched forward, tumbling over myself in the gelatin-like substance surrounding my body, and my vision began to brighten until I was completely blinded. I opened my eyes and found myself in my bed. Looking to the right I saw her, sitting at my desk.
	
	As she stood up to greet me, I could tell she had been crying. \textit{Hello}. Her voice was so quiet. \textit{I’m sorry,} I begged, \textit{I really am}. We were silent for a time. Eventually she moved to sit next to me on the bed and I put my arm around her. \textit{It’s all my fault}, she moaned, rocking back and forth. \textit{It’s not}, I countered, \textit{it was my doing, so if there is blame to lay, it is on me}. She shifted away from me after I said that and put her head in her hands. Again, we were silent for a time before we began talking. The words were terse and cut off. Something had been changed in the dynamic of our relationship that could never be reversed. We spoke at length about what John’s suicide had done to her, about how it had broken her. When there was nothing left to say, she stood up, looking troubled. \textit{You know}, she finally spoke, \textit{you aren’t real to me, you’re just in my head}. I needed some time to take that one in, my mind reeling with its implications. I stood in front of her. \textit{Well, what comes next? }I risked. She looked up at me with her huge brown eyes that I had spent hours and hours creating. As she sighed, she raised a hand and placed her palm on my chest. \textit{I think you know}, she whispered, and then leaning into me, her hand pushed through my breast, coming to rest two inches deep. She squeezed, and I felt a sharpness inside of me that made me flinch. I jolted in my bed, finally opening my eyes to the world. 
	
	I moved to my computer in a trance, the lingering pressure from Zu’s grip still tight within my chest as I began to type. I wrote for hours about her reaction to John’s death, describing in detail the torment it had put her through, how she blamed herself but didn’t exactly know why. My hands were shaking as I approached the end of my novel. She was right. I did know what came next.
\\\\
\textit{Zu celebrated her 27th birthday alone. She stood out on her balcony overlooking the city; the cool concrete was like ice on her bare feet. She looked up into the dark clouds looming over the buildings below and wondered. With a minute till midnight, her watch ticking and ticking forward as it does, she climbed onto the railing. Waiting until she heard the last click as her watch pushed ahead into the next day, she closed her eyes, pitched forward, and flew.}
